---
title: "Shiny-Example"
author: "Miguel Ortiz"
date: "September 11th, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(plotly)
```

## Football simulator

This is a presentation to show the Shiny App generated for this assignment.

- It shows a possible simulation of the result of a football match.
- It calculates the number of scores for the two teams.

## Input

As input it takes:

- Number of scores per match for team1
- Quality of team2 keeper
- Number of scores per match for team2
- Quality of team2 keeper

- Luck factor for team1


## Output 1

As output it generates a graph like this one with the scores for the two teams:

```{r cars, echo = FALSE, comment=FALSE}
data_team1 <- runif(50) * 2 + 0.2
data_team2 <- runif(50) * 4 + 0.5
df<-data.frame(team1 = data_team1, team2 = data_team2)
        
# Draw the plot using ggplot2
plot <- ggplot(df, aes(x=team1, y=team2)) + geom_point()
plot
```

## Output 2

Also it generates a tex output with the most suitable result:

```{r echo = FALSE, comment=FALSE}
res <- sprintf("The most suitable result is: %d - %d", round(max(data_team1)), round(max(data_team2)))
res
```

